---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fractals

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

Fractals is a shiny app for visualization of fractals.

## Installation

You can install the development version of fractals like so:

``` r
install.packages(devtools)
devtools::install_github("https://github.com/AnjaH8/fractals.git")
```

## Run the app

You can run the shiny app like this:
```{r, eval=FALSE}
library(fractals)
run_app()
```
In the app there is a dropdown menu where you can choose which fractal you want to display (currently only the Hilbert curve) and a slider to determine the number of iterations.

## Example

This is a basic example which shows you how you can display the Hilbert-curve after 5 iterations:

```{r example}
library(fractals)
df_hilbert <- hilbert_curve(5)
ffplot(df_hilbert)
```
